Assessment and Optimization of Nowcast Measures for Trend Detection

### 2024-01-16 paper.tex
Update on Overleaf.

\noindent
\begin{tblr}{
  colspec = {Q[h]X[-1,m]X[-1,m]X[-1,m]|X[m]},
  width=\textwidth,
  stretch = 0,
  rowsep = 6pt,
}
     & Indicator & Weighted 1 & Weighted 2 & Remarks \\
     \includegraphics{plots/simulation_comparison_weighted_measures/simple.pdf} & 0.7748 & 0.7876 & &  \\
     \includegraphics{plots/simulation_comparison_weighted_measures/concordant_no_noise.pdf} & 1 & 1 &  & {\scriptsize$\xdiff = \xdifft = 0.05 \ydifft = 0.05 \ydiff$}\newline critique on w1: slight deviation of $\xdiff$ from 0 (near decision boundary), nevertheless, full trending ability. \\
     \includegraphics{plots/simulation_comparison_weighted_measures/concordant_noise.pdf} & 0.6466 & 0.6823 & \\
     \includegraphics{plots/simulation_comparison_weighted_measures/perfect_normal.pdf} & 1 & 1 & & critique on w2: $\xdiff = \ydiff$, but not trending ability 1\\

     \includegraphics{plots/simulation_comparison_weighted_measures/sure_unsure_combination.pdf} & 0.6152 & 0.6932 & & \\
\end{tblr}

>>>>

\noindent
\begin{tblr}{
  colspec = {Q[h]X[-1,m]X[-1,m]X[-1,m]|X[m]},
  width=\textwidth,
  stretch = 0,
  rowsep = 6pt,
}
     & Indicator & Weighted 1 & Weighted 2 & Remarks \\
     \includegraphics{plots/simulation_comparison_weighted_measures/simple.pdf} & 0.7672 & 0.7836 & 0.7694 &  \\
     \includegraphics{plots/simulation_comparison_weighted_measures/concordant_no_noise.pdf} & 1 & 1 & 0.8235 & {\scriptsize$\xdiff = \xdifft = 0.05 \ydifft = 0.05 \ydiff$}\newline critique on w1: slight deviation of $\xdiff$ from 0 (near decision boundary), nevertheless, full trending ability. \\
     \includegraphics{plots/simulation_comparison_weighted_measures/concordant_noise.pdf} & 0.6466 & 0.6823 & 0.6266 & \\
     \includegraphics{plots/simulation_comparison_weighted_measures/perfect_normal.pdf} & 1 & 1 & 0.9779 & critique on w2: $\xdiff = \ydiff$, but not trending ability 1\\

     \includegraphics{plots/simulation_comparison_weighted_measures/sure_unsure_combination.pdf} & 0.6152 & 0.6932 & 0.6389 & \\
\end{tblr}
